Filmchat

### 2017-06-14 paper/paper.tex
Updated paper again

\chapterimage{head3.png}
\chapter{Interactive System: Development}
I chose to start with an implementation of Speech Recognition, as this was the initial idea of the project.
Some quick googling, and I landed on Googles Speech API (REFERENCE). There is an online tester (LINK)

@@

Next part of the development was the "omdbsearcher". Here I selected OMDB (Open Movie Database) and had to donate a couple of dollars to get access to their API. There are implementations for IMDB, but they are not, to my knowledge authorized by IMDB, and I was not interested in spending time on a non official api.

IMDB Also has some of its data dumped to a FTP on regular intervals, so creating an own database could have been a future work part for this project.

The omdbsearcher I implemented in Node JS, as this is the language I can program in fastest. I tested a couple of request with Postman (reference) which is a tool to create web requests to different endpoints. Postman also has a nice feature where you can get the code for replicating the request in different languages.

@@

@@

>>>>

\chapterimage{head3.png}
\chapter{Interactive System: Development}
\section{Overarching Goal}
The main goal for me, was to see what was possible to do, using mostly "off the shelf" components, being libraries, API's or other available premade solutions. This because the project had a limited time, and I wanted to be as effective as possible.
\section{Speech recognition}
I chose to start with an implementation of Speech Recognition, as this was the initial idea of the project.
Some quick googling, and I landed on Google's Speech API \cite{GoogleCloudPlatformSpeechPlatform}. There is an on-line tester, where you can talk, and the Web Page will print what you say.

@@

\section{Omdbsearcher}
Next part of the development was the "omdbsearcher". Here I selected OMDB (Open Movie Database) and had to donate a couple of dollars to get access to their API. There are implementations for IMDB, but they are not, to my knowledge authorized by IMDB, and I was not interested in spending time on a non official api.

IMDB Also has some of its data dumped to a FTP on regular intervals, so creating an own database could have been a future work part for this project. \cite{IMDbAlternativeInterfaces}

The Omdbsearcher I implemented in Node JS, as this is the language I can program in fastest. I tested a couple of request with Postman, which is a tool to create web requests to different endpoints. Postman also has a nice feature where you can get the code for replicating the request in different languages.

@@

\section{Textblob Botlistener}
I then checked out a couple of different ways of intepreting language, but have from other projects, already knowledge that Python has such libraries that are good, and with good performance. I therefore winded up with TextBlob, which is a library that can both get sentiment, and noun phrases\cite{WikipediaNounPhrase} from sentences. \cite{TextBlobTutorial:Documentation} 
I therefore just had to create a webservice interface for the TextBlob, and was able to do this quickly.

@@

\section{Spelling corrector}
While the Textblob Botlistener was able to get the noun phrase\cite{WikipediaNounPhrase} of sentences about movie, and that this sometimes is an actual movie, this is not always the case. Therefore I thought about using some autocorrect or spelling corrections, but using the freely available IMDB datasets as valid words \cite{IMDbAlternativeInterfaces}. I found a good example by Peter Norvig \cite{NorvigHowCorrector} on how to do it.
But both the development, and the performance was rather slow, and the dataset would have needed quite a lot of cleaning before I could have used it. Therefore I decided on not to implement this part, and to put it off to a possible future work.
